The zero--one laws of Kolmogorov and Hewitt--Savage in categorical probability

### 2019-10-24 categorical-zero-one.tex
added something on kleisli categories and infinite tensor prods

\begin{lemma}
    Let $J,J'$ be possibly infinite sets, and $\{X_i\}_{i\in J}, \{Y_i\}_{i\in J'}$ two families of objects in $\cC$, so that both have infinite tensor products with Kolmogorov extension.
    Let $\{Z_i\}_{i\in J \sqcup J'}$ be a family of objects indexed by the disjoint union, where $Z_i = X_i$ for $i\in J$, $Z_i = Y_i$ for $i \in J'$,
    and suppose $\{Z_i\}$ admits an infinite tensor product with Kolmogorov extension, too.
    Consider the family of maps
    \[\rho_F: \bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \labelto{\pi_{F \cap J} \tensor \pi_{F \cap J'}} \bigotimes_{i \in F \cap J}X_i \tensor \bigotimes_{i\in F \cap J'}Y_i\]
    indexed by finite subsets $F \subset J \sqcup J'$ of the disjoint union.
    The induced map
    \[\bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \to \bigotimes_{i \in J \sqcup J'} Z_i\]
    is a deterministic isomorphism.
\end{lemma}
\begin{proof}
    It is clear that the $\rho_F$ are deterministic, and that they form a limit diagram in $\cC_{\rm det}$.
    Hence the induced map into the actual limit in $\cC_{\rm det}$ is an isomorphism.
\end{proof}

>>>>

\begin{example}
    Suppose $\cC$ is a Cartesian monoidal category. Then it has a unique Markov category structure given by the diagonal maps,
    where every map is deterministic.
    An infinite collection of objects $\{X_i\}$ has an infinite tensor product with Kolmogorov extension if and only if it has a categorical product in $\cC$.
\end{example}

\begin{proposition}
    \todo[inline]{write proof once we've figured out the order of things. But this is one for the "wishlist"}
    Let $\cC$ be a Markov category, and let $T$ be an affine symmetric monoidal monad on $\cC$, so that the Kleisli category $Kl(T)$ is a Markov category.
    Let $\{X_i\}_{i\in J}$ be a possibly infinite family of objects in $\cC$, and suppose it has an infinite tensor product in $\cC$ with Kolmogorov extension, $\bigotimes X_i$.
    Then the limit
    \[\lim_{F \subset J} \prod_{i\in F}X_i\]
    exists in $\cC$ (by assumption, it is $\bigotimes X_i$).
    Suppose further that $T$ preserves this limit.
    Then $\bigotimes X_i$ is also an infinite tensor product of $\{X_i\}$ in $Kl(T)$.
\end{proposition}
\begin{lemma}
    Let $J,J'$ be possibly infinite sets, and $\{X_i\}_{i\in J}, \{Y_i\}_{i\in J'}$ two families of objects in $\cC$, so that both have infinite tensor products with Kolmogorov extension.
    Let $\{Z_i\}_{i\in J \sqcup J'}$ be a family of objects indexed by the disjoint union, where $Z_i = X_i$ for $i\in J$, $Z_i = Y_i$ for $i \in J'$,
    and suppose $\{Z_i\}$ admits an infinite tensor product with Kolmogorov extension, too.
    Consider the family of maps
    \[\rho_F: \bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \labelto{\pi_{F \cap J} \tensor \pi_{F \cap J'}} \bigotimes_{i \in F \cap J}X_i \tensor \bigotimes_{i\in F \cap J'}Y_i\]
    indexed by finite subsets $F \subset J \sqcup J'$ of the disjoint union.
    The induced map
    \[\bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \to \bigotimes_{i \in J \sqcup J'} Z_i\]
    is a deterministic isomorphism.
\end{lemma}
\begin{proof}
    It is clear that the $\rho_F$ are deterministic, and that they form a limit diagram in $\cC_{\rm det}$.
    Hence the induced map into the actual limit in $\cC_{\rm det}$ is an isomorphism.
\end{proof}
